---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# `{pdfparser}`


<!-- badges: start -->
<!-- badges: end -->

{pdfparser} provides tools for dealing with text extraction from PDFs.

It comes in handy when you do not only want to read in the text, for which I recommendbut also want
to deal with PDF coordinates of the words, lines and blocks.

Right now its only function is `read_bbox_layout_xhtml()` which parses XHTML files
from `pdftotext`, part of `poppler-utils` (manual can be found [here](https://www.mankier.com/1/pdftotext)).

## Installation

You can install the development version from [GitHub](https://github.com/balthasars/pdfparser) with:

``` r
# install.packages("devtools")
devtools::install_github("balthasars/pdfparser")
```
## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(pdfparser)
doc <- system.file("extdata", "edi_2009_frcho43c6mmlx5lyohqy_doc#immrrkosg.html", package = "pdfparser")
read_bbox_layout_xhtml(doc)
```
